### 2017-05-23 manuscript/usses_water_ms.Rmd
updates stats table 1

```{r caching, include=FALSE}
library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

# PDF-based figures
opts_chunk$set(dev='pdf')
```

```{r plot-options, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
               "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

opts_chunk$set(dev='pdf', dev.args=c(version="1.3"))

```

@@

```{r table, include=TRUE, comment=FALSE,warning=FALSE,message=FALSE,results='asis'}
library(xtable)
# Read in within-year ANOVA results table
inyear_anova <- readRDS("../results/within_year_anova_table.RDS")

inyear_caption <- "ANOVA for treatment effects on ANPP for each year of the experiment."
print(xtable(inyear_anova, caption = inyear_caption, digits = 2),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment = FALSE,
      size = "normalsize")
```

>>>>

```{r caching, include=FALSE}
library("methods")
library("knitr")
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)
```

@@

```{r table, include=TRUE, comment=FALSE,warning=FALSE,message=FALSE,results='asis'}
library(xtable)
# Read in within-year ANOVA results table
# inyear_anova <- readRDS("../results/within_year_anova_table.RDS")
# 
# inyear_caption <- "ANOVA for treatment effects on ANPP for each year of the experiment."
# print(xtable(inyear_anova, caption = inyear_caption, digits = 2),
#       caption.placement="top",
#       include.rownames = F, 
#       sanitize.colnames.function = identity,
#       comment = FALSE,
#       size = "normalsize")

coef_probs <- readRDS("../results/coef_probabilities.RDS")

coef_caption <- "Probability that each log(ANPP) coefficient is greater or less than zero for each of the precipitation treatments.
Probabilities denote max(Pr(coefficient) > 0, Pr(coefficient) < 0), where the sign of the coefficient was ignored. Thus, probabilities represent the probability of the coefficient being important in the model. Bold coefficients denote Pr(coefficient) $\\geq$ 0.95."
print(xtable(coef_probs, caption = coef_caption, digits = 2),
      caption.placement="top",
      include.rownames = F,
      sanitize.colnames.function = identity,
      comment = FALSE,
      size = "normalsize")
```
